Figure 4. & 5. DGE's and Enrichment

### 2022-09-30 reports/manuscript/Figure4-5.Rmd
Add library info

```{r message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(readxl)
  library(enrichR)
  library(igraph)
  library(rafalib)
})  })  })

@@

return(list(lrt=lrt, top=top, CONTRASTS=CONTRASTS))
}
################################
# PAIRWISE ENRICHMENT FUNCTION #
################################
enrich_list <- function(x, gmt_list){
  temp <- compute_enrichment(genes = x,
                            gmt_list = gmt_list,
                            min_terms_pathway = 10,
                            max_terms_pathway = 300,
                            min_overlap = 3,
                            sort_by_pvalue = T)
  temp <- temp[!grepl("REGULATION",rownames(temp)),]
  temp <- rownames_to_column(temp, var = "Terms")
  return(temp)
} 
```

@@

pages <- list(list(Across=dge_T$top), pairwise=pairwise_dge_T$top) %>% flatten()
write.xlsx(pages, file=paste0(result_dir,DEG_files[2]))
```

>>>>

```{r message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(fgsea)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(readxl)
  library(enrichR)
  library(igraph)
  library(rafalib)
})  })  })

@@

return(list(lrt=lrt, top=top, CONTRASTS=CONTRASTS))
#return(list(lrt=lrt, top=top, CONTRASTS=CONTRASTS, results=results))
}
################################
# PAIRWISE ENRICHMENT FUNCTION #
################################
enrich_list <- function(x, gmt_list){
  temp <- compute_enrichment(genes = x,
                            gmt_list = gmt_list,
                            min_terms_pathway = 10,
                            max_terms_pathway = 300,
                            min_overlap = 3,
                            sort_by_pvalue = T)
  temp <- temp[!grepl("REGULATION",rownames(temp)),]
  temp <- rownames_to_column(temp, var = "Terms")
  return(temp)
} 
```

@@

pages <- list(list(Across=dge_T$top), pairwise=pairwise_dge_T$top) %>% flatten()
write.xlsx(pages, file=paste0(result_dir,DEG_files[2]))

#Files with filtered p-value < 0.01 
# Have to update the summary table, however the decideTests
# function does not provide support for p-value cutoffs only FDR
# therefore I need to write code to get the correct summary

p_L <- map(pairwise_dge_L$top[-1], ~filter(.x, `PValue`<0.01))
p_T <- map(pairwise_dge_T$top[-1], ~filter(.x, `PValue`<0.01))

pages <- list(list(Across=dge_L$top), pairwise=p_L) %>% flatten()
write.xlsx(pages, file=paste0(result_dir,DEG_files[1]))

pages <- list(list(Across=dge_T$top), pairwise=p_T) %>% flatten()
write.xlsx(pages, file=paste0(result_dir,DEG_files[2]))
```
